Poseidon Adventure

### 2019-05-14 docs/index.Rmd
add NEUS example
add lf from standard survey

>>>>

<a href="https://sgaichas.github.io/poseidon-dev/NEUSTrueLengthCompTest.html" target="_blank">NEUS length composition examples - May 13, 2019</a>

Standard survey with length sampling: impact of selectivity, `sample_fish`

<a href="https://sgaichas.github.io/poseidon-dev/StdSurvLengthCompTest.html" target="_blank">Compare survey + sampled lengths with true - May 14, 2019</a>
